Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-21 docs/papers/roofline_model/gocean_roofline.tex
roofline: updates with linpack/stream results on Archer and desktop

CPU name:       Intel(R) Xeon(R) CPU E5-1620 v2 @ 3.70GHz
CPU type:       Intel Xeon IvyBridge EN/EP/EX processor

Level 1 32 kB
Level 2 256 kB
Level 3 10 MB

@@

In applying the roofline model we follow the approach suggested
in~\cite{para_pearls} and use the well-known STREAM~\cite{stream} and
LINPACK~\cite{linpack} benchmarks in order to get the upper bounds on
the memory bandwidth and FLOPS for the test hardware. Since we are
using an Intel CPUs we used the Intel Math Kernel Library
implementation of LINPACK.

@@

>>>>

In applying the roofline model we follow the approach suggested
in~\cite{para_pearls} and use the well-known STREAM~\cite{stream} and
LINPACK~\cite{linpack} benchmarks in order to get the upper bounds on
the memory bandwidth and FLOPS for the test hardware. Since we are
using Intel CPUs we used the Intel Math Kernel Library
implementation of LINPACK.

\begin{table}
\begin{tabular}{l|c|c|c|c}
  & \multicolumn{2}{c|}{E5-1620 v.~2, 3.7GHz} & \multicolumn{2}{c}{E5-2697 v.~2, 2.7GHz}  \\
  \hline
  L2 Cache (KB)             & \multicolumn{2}{c|}{256} &  \multicolumn{2}{c}{256}  \\
  L3 Cache (MB)             & \multicolumn{2}{c|}{10}  &  \multicolumn{2}{c}{30}  \\
  \hline
  Array size ($10^6$ words) &   0.25 &  5      &  0.25  & 0.5    & 15 \\
  STREAM, Triad (GB/s)      &  35.49 & 17.64   & 29.271 & 13.8426 & 9.6218 \\
  \hline
 LINPACK (GFLOPS)      & \multicolumn{2}{c|}{28.32}  & \multicolumn{2}{c}{25.41} \\
\hline
\end{tabular}
\caption{The STREAM and LINPACK benchmark results for a single thread
  running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=120mm]{nemolite2d_kernel_perf}
  \caption{Performance of the Continuity and u-Momentum kernels as a
    function of SIMD vectorisation and problem size. Results are for
    v.16 of the Intel compiler on a Xeon E5-1620 v.2 CPU.}
  \label{FIG_kernel_perf}
\end{figure}
